Tugas UTS

### 2024-02-26 Project/Tugas UTS.Rmd
Update

@@

#2. Jacknife Sampling
y <- matrix(NA, n, n-1)
x <- matrix(NA, n, n-1)
for (i in 1:n) {
  y[i,] <- d1$item1[-i]
  x[i,] <- d1$item2[-i]
}
ybar <- apply(y, 1, mean)
xbar <- apply(x, 1, mean)
teta_i <- ybar/ (xbar+ybar)
teta_jk <-n *teta_hat -(n-1) *mean(teta_i)
var_jk <- (n-1)/ n *(sum(teta_i^2) -(n *mean(teta_i)^2))
se_jk <- sqrt(var_jk)
teta_jk; var_jk; se_jk
```

>>>>

Sehingga banyaknya ulangan yang dapat dilakukan adalah sebanyak n.

@@

#2. Jacknife Sampling
y <- matrix(NA, n, n-1)
x <- matrix(NA, n, n-1)
for (i in 1:n) {
  y[i,] <- d1$item1[-i]
  x[i,] <- d1$item2[-i]
}

ybar <- apply(y, 1, mean)
xbar <- apply(x, 1, mean)
teta_i <- ybar/ (xbar+ybar)
teta_jk <-n *teta_hat -(n-1) *mean(teta_i)
var_jk <- (n-1)/ n *(sum(teta_i^2) -(n *mean(teta_i)^2))
se_jk <- sqrt(var_jk)
teta_jk; var_jk; se_jk
```
